---
title: "Regular update for DEE2 database"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 7
theme: cosmo
---

## Intro

This script updates the DEE2 database with the newly processed datasets.
It is important for QC and aggregating the datasets.

Notes

* if an error occurs on here: mclapply(fin_new,check_contents,gre,tre,mc.cores=CORES)
 then need to run this rm -rf `find ../data/org | grep tmp$ | head -1000`

Set the organism

The following code can take user supplied arguments and run the pipeline.

```
args = commandArgs(trailingOnly=TRUE)
org=args[1]
print(org)
```

We could run this as a for loop from bash

```
for ORG in athaliana osativa zmays celegans dmelanogaster drerio rnorvegicus scerevisiae ecoli hsapiens mmusculus
bdistachyon gmax hvulgare ptrichocarpa sbicolor slycopersicum stuberosum taestivum vvinifera ; do

  Rscript -e "rmarkdown::render('dee_pipeline.Rmd')" $ORG

done

```

It can also be run in R like this:

```
#rmarkdown::render("dee_pipeline.Rmd",params=list(org = "ecoli"))
```


```{r,begin}

setwd("/mnt/hdd1/dee2/code")

library("parallel")
library("data.table")
library("R.utils")
library("reutils")
library("XML")
library("rjson")
library("rhdf5")
library("reutils")

IPADD="118.138.235.221"

CORES=5

#start the analysis

#for ( org in c( "athaliana", "osativa", "zmays",
# "celegans", "dmelanogaster", "drerio",
#"rnorvegicus", "scerevisiae" , "mmusculus", "ecoli", "hsapiens" )) {

args = commandArgs(trailingOnly=TRUE)
#org=args[1]
org="athaliana"

species_list <- c("3702", "4530", "4577", "6239", "7227", "7955",
  "562", "9606", "10090", "10116", "4932",
  "15368", "3847", "1753", "3694", "4558",
  "1753", "4113", "4565", "1753")

#now annotate the short names 
names(species_list) <- c("athaliana", "osativa", "zmays",
  "celegans", "dmelanogaster", "drerio",
  "ecoli", "hsapiens", "mmusculus", "rnorvegicus", "scerevisiae",
  "bdistachyon", "gmax", "hvulgare", "ptrichocarpa", "sbicolor",
  "slycopersicum", "stuberosum", "taestivum", "vvinifera")

taxa_name <- species_list[[org]]

species_names <- c("'Arabidopsis thaliana'", "'Oryza sativa'",
  "'Zea mays'", "'Caenorhabditis elegans'",
  "'Drosophila melanogaster'", "'Danio rerio'",
  "'Escherichia coli'", "'Homo sapiens'", "'Mus musculus'",
  "'Rattus norvegicus'", "'Saccharomyces cerevisiae'",
  "'Brachypodium distachyon'", "'Glycine max'",
  "'Hordeum vulgare'", "'Populus trichocarpa'",
  "'Sorghum bicolor'","'Solanum lycopersicum'",
  "'Solanum tuberosum'", "'Triticum aestivum'",
  "'Vitis vinifera'")

#now annotate the short names 
names(species_names)<- c("athaliana", "osativa", "zmays",
  "celegans", "dmelanogaster", "drerio",
  "ecoli", "hsapiens", "mmusculus", "rnorvegicus", "scerevisiae",
  "bdistachyon", "gmax", "hvulgare", "ptrichocarpa", "sbicolor",
  "slycopersicum", "stuberosum", "taestivum", "vvinifera")

species_name <- species_names[[org]]

print(org)

#number of protein coding genes from ensembl
numgenes <- c(27655, 35806, 39756, 20362, 13918, 25903, 4140, 20338, 22598, 22250, 6692,
  34310, 55897, 35826, 34699, 34118, 34658, 39021, 107891, 37480)

names(numgenes) <- c("athaliana", "osativa", "zmays",
  "celegans", "dmelanogaster", "drerio",
  "ecoli", "hsapiens", "mmusculus", "rnorvegicus", "scerevisiae",
  "bdistachyon", "gmax", "hvulgare", "ptrichocarpa", "sbicolor",
  "slycopersicum", "stuberosum", "taestivum", "vvinifera")

numgenes = numgenes[[org]]

###Set some directories
CODEWD = getwd()
DATAWD = paste(normalizePath("../data/"),org,sep="/")
SRADBWD = normalizePath("../sradb/")
MXDIR = normalizePath("../mx/")
QUEUEWD = normalizePath("../queue/")

### Set years range
YEARS=2000:2025

```

## Get metadata 

For human and mouse, we may need to fetch the metadata in chunks that are grouped by year.

`
pysradb search --organism="Homo sapiens"  --publication-date 01-01-2015:31-12-2020 --source="transcriptomic" --max=999000 --saveto hsapiens_test2020.csv
`

Using a helper bash script called metadata_dl.sh which uses pysradb.
It grabs monthly batches of metadata.

Previously I fetched all data 2024 and before, and so now I only need to get 2025 data fresh.

This means that each january this script should be updated.

```{r,fetchmetadata}

CSVOLD=paste(SRADBWD,"/",org,"_2024.csv",sep="")

CSVNEW=paste(SRADBWD,"/",org,"_2025.csv",sep="")

if (file.exists(CSVNEW)) {
  FILENAME=gsub(".csv","_old.csv",CSVNEW)
  renameFile(CSVNEW,FILENAME,overwrite=TRUE)
}

MY_SRA_CMD <- paste('bash metadata_dl_2025.sh', org)
MY_SRA_CMD
system(MY_SRA_CMD)

if (!file.exists(CSVNEW)) {
    stop("Error: the metadata CSV file does not exist")
}

res1 <- read.csv(CSVNEW,stringsAsFactors=FALSE)
res0 <- read.csv(CSVOLD,stringsAsFactors=FALSE,header=FALSE)
colnames(res0) <- colnames(res1)
res0 <- res0[which(res0$study_accession!="study_accession"),]
res <- rbind(res0,res1)
COLS <- colnames(res)

if ( "run_1_accession" %in% COLS ) {

  res <-res[order(res$run_1_accession),]
  dim(res)
  res <- unique(res)
  dim(res)

  accessions <- as.data.frame(cbind(res$experiment_accession,
    res$study_accession,
    res$sample_accession,
    res$run_1_accession))

} else {

  res <-res[order(res$Run),]
  dim(res)
  res <- unique(res)
  dim(res)

  accessions <- as.data.frame(cbind(res$Experiment,
    res$SRAStudy,
    res$Sample,
    res$Run))

}

accessions <- unique(accessions)
nrow(accessions)
colnames(accessions) <- c("experiment","study","sample","run")
runs <- accessions$run
source("dee_pipeline_functions.R")

```

## Now determine which datasets have already been processed and completed

```{r,check_presence_new_datasets}

unlink(list.files(DATAWD,pattern="_STARtmp",recursive=T))

folders<-list.files(DATAWD,full.names=T,pattern="RR")
fin_new<-paste(DATAWD,sapply(strsplit(list.files(path = DATAWD, pattern = "finished" ,
  full.names = T, recursive = T),"/"),"[[",7),sep="/")
fin_new<-fin_new[grep("RR",fin_new)]
val_old<-paste(DATAWD,sapply(strsplit(list.files(path = DATAWD, pattern = "validated" ,
  full.names = T, recursive = T),"/"),"[[",7),sep="/")

# delete folders that are not expected as they are not in known runs
expected_folders<-paste(DATAWD,runs,sep="/")
unexpected_folders<-setdiff(folders,expected_folders)
write(unexpected_folders,file=paste(DATAWD,"/unexpected_folders.txt",sep=""))

# delete folders without finished or validated files
allocated<-union(fin_new,val_old)
unalloc<-setdiff(folders,allocated)
unlink(unalloc,recursive=TRUE)

#Expected rows of se and ke files
gre<-dim( read.table(paste(DATAWD,"/rownames_gene.txt",sep=""),header=TRUE, comment.char="") )[1]
tre<-dim( read.table(paste(DATAWD,"/rownames_tx.txt",sep=""),header=TRUE, comment.char="") )[1]

message("run the check of new datasets")
source("dee_pipeline_functions.R")

mclapply(fin_new,check_contents,gre,tre,mc.cores=CORES)
message("done")

val<-paste(DATAWD,sapply(strsplit(list.files(path = DATAWD, pattern = "validated" ,
  full.names = T, recursive = T),"/"),"[[",7),sep="/")
runs_done<-sapply(strsplit(val,"/"),"[[",7)

se_files<-paste( DATAWD , "/" , runs_done , "/" , runs_done , ".se.tsv.gz",sep="")

print(paste(length(runs_done),"runs completed"))
runs_todo<-base::setdiff(runs, runs_done)
print(paste(length(runs_todo),"requeued runs"))

# Cut the queue and flip order sometimes, so that we can analyse different runs
# and not just process the same ones again and again
CUTPOINT=sample(1:length(runs_todo),1)
runs_todo <- runs_todo[c(CUTPOINT:length(runs_todo),1:(CUTPOINT-1))]
ORIENTATION <- as.numeric(format(Sys.time(), "%s")) %% 2
if ( ORIENTATION == 0 ) {  runs_todo <- rev(runs_todo) }

#Update queue on webserver if older than
queue_name=paste(QUEUEWD,"/",org,".queue.txt",sep="")
write.table(runs_todo,queue_name,quote=F,row.names=F,col.names=F)
SCP_COMMAND=paste("scp -i ~/.ssh/dee2_2025 ",queue_name ," ubuntu@118.138.235.221:~/Public")
system(SCP_COMMAND)

#Update metadata on webserver
accessions_done<-accessions[which(accessions$run %in% runs_done),] #thisline audit
write.table(accessions_done,file=paste(SRADBWD,"/",org,"_accessions.tsv",sep=""),quote=F,row.names=F)

save.image(file = paste(org,".RData",sep=""))

```

## Get GEO metadata information

Again any data from 2022 or earlier has been previously downloaded so we only need to download 2023 data.

```{r,geoquery1}

gq <- paste("Rscript geoquery.R",org)

system(gq)

```

## Now to tidy up the metadata from GEO

```{r,tidymetadata1}

GEONEW=paste(SRADBWD,"/",org,"_all.csv",sep="")

gse <- read.table(GEONEW,sep=",")

resx <- merge(res,gse,by.x="sample_alias",by.y="GEO_sample",all.x=TRUE)

# here is a good opportunity to check that the join has worked
res<-resx
res<-res[order(res$run_1_accession),]

QC_summary <- "NA"

#extract out the important accessions in order
x2<-as.data.frame(cbind(res$run_1_accession, QC_summary, res$experiment_accession,
  res$sample_accession, res$study_accession,res$experiment_title,
  res$GEO_series), stringsAsFactors=FALSE)

colnames(x2)<-c("SRR_accession","QC_summary","SRX_accession","SRS_accession",
  "SRP_accession","Experiment_title","GEO_series")

# NA values replaced with blank
x2[is.na(x2)] <- ""

#write out the accession number info and upload to webserver
write.table(x2,file=paste(SRADBWD,"/",org,"_metadata.complete.tsv.cut",sep=""),
  quote=F,sep="\t",row.names=F)
x2<-x2[which(x2$SRR_accession %in% runs_done),]

# write the srpqueue to enable new request from users
srpqueue <- accessions[which(! accessions$run %in% x2$SRR_accession),2]
srpqueue <- unique(srpqueue)
srpqueue <- srpqueue[order(srpqueue)]
srpqueuename = paste(SRADBWD,"/",org,"_srpqueue.txt",sep="")
writeLines(srpqueue,con=srpqueuename)
SCP_COMMAND=paste("scp -i ~/.ssh/dee2_2025", srpqueuename ,
    " ubuntu@118.138.235.221:/dee2_data/srpqueue")
system(SCP_COMMAND)

```

## Quality control

```{r,qc1}

source("dee_pipeline_functions.R")
library("parallel")

# this line was giving some errors with mouse data - now executes in batches
myaccessions <- x2$SRR_accession
length(myaccessions)
qc_res=NULL
chunksize=200
while (length(myaccessions) > chunksize ) {
  qc_res_part<-unlist(mclapply(myaccessions[1:chunksize], qc_analysis, org=org,
    mc.cores=CORES))
  qc_res <- c(qc_res,qc_res_part)
  myaccessions <- myaccessions[(chunksize+1):length(myaccessions)]
}

if (length(myaccessions) > 0 ) {
  qc_res_part<-unlist(mclapply(myaccessions, qc_analysis, org=org,mc.cores=CORES))
  qc_res <- c(qc_res,qc_res_part)
}
x2$QC_summary <- qc_res

# write metadata
write.table(x2,file=paste(SRADBWD,"/",org,"_metadata.tsv.cut",sep=""),
  quote=F,sep="\t",row.names=F)

```

## Data aggregation

SE, KE, then QC files in HDF5 format.

```{r,dataagg_hdf5}

CORES=4

h5file <- paste(org,"_se.h5",sep="")
if (file.exists(h5file)) { file.remove(h5file) }
h5createFile(h5file)
srr <- x2$SRR_accession
file_list <- paste("/mnt/hdd1/dee2/data/",org,"/",srr,"/",srr,".se.tsv.gz",sep="")
batch_size <- 500
num_files <- length(file_list)
rows_per_file <- nrow(read.table(file_list[1],row.names=1,header=TRUE))
num_cols <- 1
h5createDataset(
  file = h5file,
  dataset = "bigmatrix",
  dims = c(num_files, rows_per_file),
  storage.mode = "integer",
  chunk = c(10, rows_per_file),    # 10,000-row chunks
  level = 9                      # compression level (gzip)
)
for (i in seq(1, length(file_list), by = batch_size)) {
  batch_files <- file_list[i:min(i + batch_size - 1, length(file_list))]
  data_list <- mclapply(batch_files, function(f) {
    t(as.matrix(read.table(f,header=TRUE,row.names=1)[,1]))
  } , mc.cores=CORES )
  batch_data <- do.call(rbind, data_list)
  row_start <- (i - 1) + 1
  row_end <- row_start + nrow(batch_data) - 1
  h5write(batch_data, h5file, "bigmatrix", index = list(row_start:row_end, 1:rows_per_file ))
  cat(sprintf("Processed files %d to %d\n", i, i + length(batch_files) - 1))
}
myrownames <- sapply(strsplit(basename(file_list),"\\."),"[[",1)
h5write(myrownames, h5file,"rownames")
mycolnames <- rownames( read.table(file_list[1]) )
h5write(mycolnames, h5file, "colnames")
H5close()
system(paste('rsync -azh -e \"ssh -i  ~/.ssh/dee2_2025 \" ', h5file ,' ubuntu@dee2.io:/dee2_data/bulk/',sep=""))
copyFile(h5file,"../mx/",overwrite=TRUE)
unlink(h5file)

# NOW FOR THE KE TSV DATASET
h5file <- paste(org,"_ke.h5",sep="")
if (file.exists(h5file)) { file.remove(h5file) }
h5createFile(h5file)
file_list <- paste("/mnt/hdd1/dee2/data/",org,"/",srr,"/",srr,".ke.tsv.gz",sep="")
batch_size <- 500
num_files <- length(file_list)
rows_per_file <- nrow(read.table(file_list[1],row.names=1,header=TRUE))
num_cols <- 1
 h5createDataset(
  file = h5file,
  dataset = "bigmatrix",
  dims = c(num_files, rows_per_file),
  storage.mode = "double",
  chunk = c(10, rows_per_file),    # 10,000-row chunks
  level = 9                      # compression level (gzip)
)
for (i in seq(1, length(file_list), by = batch_size)) {
  batch_files <- file_list[i:min(i + batch_size - 1, length(file_list))]
  data_list <- mclapply(batch_files, function(f) {
    t(as.matrix(read.table(f,header=TRUE,row.names=1)[,3]) )
  } , mc.cores=CORES )
  batch_data <- do.call(rbind, data_list)
  row_start <- (i - 1) + 1
  row_end <- row_start + nrow(batch_data) - 1
  h5write(batch_data, h5file, "bigmatrix", index = list(row_start:row_end, 1:rows_per_file ))
  cat(sprintf("Processed files %d to %d\n", i, i + length(batch_files) - 1))
}
myrownames <- sapply(strsplit(basename(file_list),"\\."),"[[",1)
h5write(myrownames, h5file, "rownames")
mycolnames <- rownames( read.table(file_list[1]) )
h5write(mycolnames, h5file, "colnames")
H5close()
system(paste('rsync -azh -e \"ssh -i  ~/.ssh/dee2_2025 \" ', h5file ,' ubuntu@dee2.io:/dee2_data/bulk/',sep=""))
copyFile(h5file,"../mx/",overwrite=TRUE)
unlink(h5file)


## Next is the QC data
h5file <- paste(org,"_qc.h5",sep="")
if (file.exists(h5file)) { file.remove(h5file) }
h5createFile(h5file)
file_list <- paste("/mnt/hdd1/dee2/data/",org,"/",srr,"/",srr,".qc",sep="")
batch_size <- 10000
qc <- read.csv(file_list[1],row.names=1,header=FALSE,sep=":")
num_files <- length(file_list)
rows_per_file <- nrow(read.csv(file_list[1],row.names=1,header=FALSE,sep=":"))
num_cols <- 1
h5createDataset(
  file = h5file,
  dataset = "bigmatrix",
  dims = c(num_files, rows_per_file),
  storage.mode = "character",
  chunk = c(100, rows_per_file),
  level = 9
)
for (i in seq(1, length(file_list), by = batch_size)) {
  batch_files <- file_list[i:min(i + batch_size - 1, length(file_list))]
  data_list <- mclapply(batch_files, function(f) {
    t(as.matrix( read.csv(f,row.names=1,header=FALSE,sep=":") ) )
  } , mc.cores=CORES )
  batch_data <- do.call(rbind, data_list)
  row_start <- (i - 1) + 1
  row_end <- row_start + nrow(batch_data) - 1
  h5write(batch_data, h5file, "bigmatrix", index = list(row_start:row_end, 1:rows_per_file ))
  cat(sprintf("Processed files %d to %d\n", i, i + length(batch_files) - 1))
}
myrownames <- sapply(strsplit(basename(file_list),"\\."),"[[",1)
h5write(myrownames, h5file, "rownames")
mycolnames <- rownames( read.table(file_list[1]) )
h5write(mycolnames, h5file, "colnames")
H5close()
system(paste('rsync -azh -e \"ssh -i  ~/.ssh/dee2_2025 \" ', h5file ,' ubuntu@dee2.io:/dee2_data/bulk/',sep=""))
copyFile(h5file,"../mx/",overwrite=TRUE)
unlink(h5file)

```

Make md5sums and send to server.

```{r,dataagg_legacy}

#aggregate se ke and qc data
CMD=paste("./dee_pipeline.sh",org)
system(CMD)

```

## Transfer the data files to the webserver

```{r,transfer1}

#delete *e.tsv.gz after each chunk of 10000
#not needed if --exclude \"*.gz\" is used
CMD2=paste('ssh -i ~/.ssh/dee2_2025 ubuntu@dee2.io "find /dee2_data/data/',org,' | grep e.tsv.gz | parallel -j1 rm {}"',sep="")

#here we rsync files to server in chunks of 50000
rsync<-function(d,org) {
  while ( length(d)>0 ) {
    CHUNKSIZE=10000
    if ( length(d)>CHUNKSIZE ) {
      chunk<-paste(d[1:CHUNKSIZE],collapse=" ")
      d<-setdiff(d,d[1:CHUNKSIZE])
    } else {
      chunk<-paste(d[1:length(d)],collapse=" ")
      d<-setdiff(d,d[1:CHUNKSIZE])
    }
    CMD=paste('rsync -azh -e \"ssh -i  ~/.ssh/dee2_2025 \" --exclude \"*.gz\" ', chunk ,' ubuntu@dee2.io:/dee2_data/data/',org,sep="")
    writeLines(CMD,"cmd")
    system("bash cmd")
    unlink("cmd")
    system(CMD2)
    message(length(d))
  }
}
d<-val
rsync(d,org)

#now attach the additional metadata and upload
x<-res[, !(colnames(res) %in%
  c("QC_summary","Experiment","sample_acc","SRA.Study","GEO_series","GEO_Accession"))]
x<-merge(x2,x,by.x="SRR_accession",by.y="run_1_accession")

x<-x[which(x$SRR_accession %in% runs_done),]
x <- apply(x,2,as.character)
x<-gsub("\r?\n|\r", " ", x)
write.table(x,file=paste(SRADBWD,"/",org,"_metadata.tsv",sep=""),quote=F,sep="\t",row.names=F)

SCP_COMMAND=paste("scp -i ~/.ssh/dee2_2025 ", paste(SRADBWD,"/",org,"_metadata.tsv",sep="") , " ubuntu@dee2.io:/dee2_data/metadata")
system(SCP_COMMAND)

SCP_COMMAND=paste("scp -i ~/.ssh/dee2_2025 ", paste(SRADBWD,"/",org,"_metadata.tsv.cut",sep="") , " ubuntu@dee2.io:/dee2_data/metadata")
system(SCP_COMMAND)

save.image(file = paste(org,".RData",sep=""))

```

## Update the dataset numbers on the dee2.io website

This is the last step.

```{r, updatepng}

FILES1 <- list.files(pattern="*metadata.complete.tsv.cut$",path="/mnt/hdd1/dee2/sradb/",full.names=T)
x <- as.data.frame(sapply(FILES1,rowcnt2),stringsAsFactors=FALSE)

rownames(x)=c("A. thaliana", "B. distachyon", "C. elegans",
  "D. melanogaster", "D. rerio", "E. coli", "G. max",
  "H. sapiens", "H. vulgare", "M. musculus", "O. sativa",
  "P. trichocarpa", "R. norvegicus", "S. bicolor",
  "S. cerevisiae", "S. lycopersicum", "S. tuberosum",
  "T. aestivum", "V. vinifera", "Z. mays")

colnames(x)="queued"

FILES2 <- list.files(pattern="*_metadata.tsv$",path="/mnt/hdd1/dee2/sradb/",full.names=T)
y <- as.data.frame(sapply(FILES2,rowcnt2),stringsAsFactors=FALSE)

rownames(y)=c("A. thaliana", "B. distachyon", "C. elegans",
  "D. melanogaster","D. rerio", "E. coli", "G. max",
  "H. sapiens", "H. vulgare", "M. musculus", "O. sativa",
  "P. trichocarpa", "R. norvegicus", "S. bicolor",
  "S. cerevisiae", "S. lycopersicum", "S. tuberosum",
  "T. aestivum", "V. vinifera", "Z. mays")

colnames(y) = "completed"

z <- merge(x,y,by=0)
rownames(z) = z$Row.names
z$Row.names = NULL

zz <- as.data.frame(apply(z,2,as.numeric))
zz$queued <- zz$queued - zz$completed
rownames(zz) <- rownames(z)
z <- zz

DATE = date()
HEADER = paste("Updated",DATE)
z <- z[order(rownames(z),decreasing=T ), ,drop=F]

plants <- c("Z. mays", "V. vinifera", "T. aestivum","S. tuberosum","S. lycopersicum", "S. bicolor",
  "P. trichocarpa","O. sativa","H. vulgare","G. max","B. distachyon","A. thaliana")

animals <- c("R. norvegicus","M. musculus", "H. sapiens", "D. rerio", "D. melanogaster", "C. elegans")

microbes <- c("S. cerevisiae","E. coli")

plantdf <- z[rownames(z) %in% plants,]
animaldf <- z[rownames(z) %in% animals,]
microbedf <- z[rownames(z) %in% microbes,]

png("dee_datasets.png",width=600,height=600)
options(bitmapType="cairo")
layout.matrix <- matrix(c(1, 3, 2, 2), nrow = 2, ncol = 2)

layout(mat=layout.matrix, heights=c(2,1),widths=c(2,2))

par(las=2) ; par(mai=c(0.5,2,0.5,0.2))
MAX=1000000
z2 <- animaldf
bb <- barplot( t(z2), beside=TRUE , xlim=c(0,MAX), main="Animals", col=c("#FFDD00","#0057B7") ,
  horiz=T , las=1, cex.axis=1.2, cex.names=1.3, cex.main=1.4, xlab="number of SRA runs")
legend("topright", rev(colnames(z2)), fill=c("#0057B7","#FFDD00") , cex=1.1)
text( cbind(as.numeric(z2[,1])+150000 ,as.numeric(z2[,2])+150000 ),
  t(bb),labels=c(z2[,1],z2[,2]) ,cex=1.15)

par(las=2) ; par(mai=c(0.5,2,0.5,0.2))
MAX=150000
z2 <- plantdf
bb <- barplot( t(z2), beside=TRUE , xlim=c(0,MAX), main="Plants", col=c("#FFDD00","#0057B7") ,
  horiz=T , las=1, cex.axis=1.2, cex.names=1.3, cex.main=1.4, xlab="number of SRA runs")
mtext(HEADER, las=1, adj=1, cex=0.8)
text( cbind(as.numeric(z2[,1])+20000 ,as.numeric(z2[,2])+20000 ),
  t(bb),labels=c(z2[,1],z2[,2]) ,cex=1.15)

par(las=2) ; par(mai=c(0.5,2,0.5,0.2))
MAX=55000
z2 <- microbedf
bb <- barplot( t(z2), beside=TRUE , xlim=c(0,MAX), main="Microbes", col=c("#FFDD00","#0057B7"),
horiz=T , las=1, cex.axis=1.2, cex.names=1.3, cex.main=1.4, xlab="number of SRA runs")
text( cbind(as.numeric(z2[,1])+8000 ,as.numeric(z2[,2])+8000 ),
  t(bb),labels=c(z2[,1],z2[,2]) ,cex=1.15)

dev.off()

system("scp -i ~/.ssh/dee2_2025 dee_datasets.png ubuntu@dee2.io:/home/ubuntu/dee2/frontend/html/images")


animaldf$group="Animal"
plantdf$group="Plant"
microbedf$group="Microbe"
df <- rbind(animaldf,plantdf,microbedf)
df$pc_complete <- signif(df$completed /  (df$completed +  df$queued) *100 ,3)

df <- df[,c(3,1,2,4)]
colnames(df) <- c("Group","Queued","Completed","% Complete")

library(gridExtra)
library(gtable)
library(grid)

# Sample data
data <- data.frame(
  System = c("Neural Link", "Cyber Deck", "Bio Monitor", "Optic Array"),
  Status = c("ACTIVE", "STANDBY", "ACTIVE", "OFFLINE"),
  Capacity = c("98%", "76%", "100%", "0%"),
  Uptime = c("247h", "180h", "312h", "0h")
)

# Cyberpunk color scheme
bg_dark <- "#0a0e27"
bg_header <- "#1a1f3a"
text_cyan <- "#00ffff"
text_magenta <- "#ff00ff"
text_green <- "#39ff14"
text_red <- "#ff0055"
border_neon <- "#00ffff"

# Custom theme function
cyberpunk_theme <- ttheme_minimal(
  core = list(
    fg_params = list(
      col = text_cyan,
      fontface = "bold",
      fontfamily = "mono",
      cex = 1.1
    ),
    bg_params = list(
      fill = c(rep(c(bg_dark, "#0f1435"), length.out = nrow(data))),
      col = border_neon,
      lwd = 2
    )
  ),
  colhead = list(
    fg_params = list(
      col = text_magenta,
      fontface = "bold",
      fontfamily = "mono",
      cex = 1.2
    ),
    bg_params = list(
      fill = bg_header,
      col = border_neon,
      lwd = 3
    )
  ),
  rowhead = list(
    fg_params = list(col = text_green),
    bg_params = list(
      fill = bg_header,
      col = border_neon
    )
  )
)

# Draw the table
png("dee_datasets2.png",width=480,height=550,bg=NA)
grid.newpage()
grid.rect(gp = gpar(fill = bg_dark, col = NA))
g <- tableGrob(df, theme = cyberpunk_theme)

# Add neon glow effect (outer border)
g <- gtable_add_grob(
  g,
  grobs = rectGrob(gp = gpar(col = text_magenta, fill = NA, lwd = 4)),
  t = 1, l = 1, b = nrow(g), r = ncol(g),
  z = 0
)
grid.draw(g)

# Add title with glow effect
grid.text(
  "⚡ DEE2 Data by SRA Run ⚡",
  x = 0.5, y = 0.95,
  gp = gpar(
    col = text_cyan,
    fontsize = 20,
    fontface = "bold",
    fontfamily = "mono"
  )
)

dev.off()
system("scp -i ~/.ssh/dee2_2025 dee_datasets2.png ubuntu@dee2.io:/home/ubuntu/dee2/frontend/html/images")

```


Grab bundles

```{r,bundles1}

bundles <- list.files("../sradb/big_proj/",pattern="*zip$",recursive=TRUE)

bundle_tbl <- table(sapply(strsplit(bundles,"/"),"[[",1))

names(bundle_tbl) <- c("A. thaliana", "B. distachyon", "C. elegans",
  "D. melanogaster","D. rerio", "E. coli", "G. max",
  "H. sapiens", "H. vulgare", "M. musculus", "O. sativa",
  "P. trichocarpa", "R. norvegicus", "S. bicolor",
  "S. cerevisiae", "S. lycopersicum", "S. tuberosum",
  "T. aestivum", "V. vinifera", "Z. mays")

animal_bundles <- bundle_tbl[names(bundle_tbl) %in% animals]
plant_bundles <- bundle_tbl[names(bundle_tbl) %in% plants]
microbe_bundles <- bundle_tbl[names(bundle_tbl) %in% microbes]

animal_bundles <- data.frame(animal_bundles,row.names=names(animal_bundles))
plant_bundles <- data.frame(plant_bundles,row.names=names(plant_bundles))
microbe_bundles <- data.frame(microbe_bundles,row.names=names(microbe_bundles))

animal_bundles$Var1 <- "Animal"
plant_bundles$Var1 <- "Plant"
microbe_bundles$Var1 <- "Microbe"

bundle_tbl2 <- rbind(animal_bundles,plant_bundles,microbe_bundles)
colnames(bundle_tbl2) <- c("Group","No. bundles")

df2 <- bundle_tbl2

# Draw the table
png("dee_bundles.png",width=480,height=550,bg=NA)
grid.newpage()
grid.rect(gp = gpar(fill = bg_dark, col = NA))
g <- tableGrob(df2, theme = cyberpunk_theme)

# Add neon glow effect (outer border)
g <- gtable_add_grob(
  g,
  grobs = rectGrob(gp = gpar(col = text_magenta, fill = NA, lwd = 4)),
  t = 1, l = 1, b = nrow(g), r = ncol(g),
  z = 0
)
grid.draw(g)

# Add title with glow effect
grid.text(
  "⚡ DEE2 Data Bundles ⚡",
  x = 0.5, y = 0.95,
  gp = gpar(
    col = text_cyan,
    fontsize = 20,
    fontface = "bold",
    fontfamily = "mono"
  )
)

dev.off()
system("scp -i ~/.ssh/dee2_2025 dee_bundles.png ubuntu@dee2.io:/home/ubuntu/dee2/frontend/html/images")

```

```{r,bundles}

CMD_BUNDLES <- paste("bash bundles.sh",org)
system(CMD_BUNDLES)

library(rentrez)
library(xml2)
library(jsonlite)

get_sra_studies_metadata_xml2 <- function(study_accessions) {
  results <- list()

  for (accession in study_accessions) {
    cat("Fetching:", accession, "\n")

    tryCatch({
      # Search for the study
      search_result <- entrez_search(
        db = "sra",
        term = paste0(accession, "[Accession]"),
        retmax = 100
      )

      if (length(search_result$ids) > 0) {
        # Fetch XML data
        xml_data <- entrez_fetch(
          db = "sra",
          id = search_result$ids[1],
          rettype = "xml"
        )

        # Parse XML with xml2
        doc <- read_xml(xml_data)

        # Helper function to safely extract values
        safe_extract_xml2 <- function(xpath_expr, doc) {
          result <- xml_find_all(doc, xpath_expr)
          if (length(result) == 0) {
            return(NA)
          } else if (grepl("@", xpath_expr)) {
            # It's an attribute
            return(xml_text(result[1]))
          } else {
            # It's an element
            return(xml_text(result[1]))
          }
        }

        study_info <- list(
          accession = accession,
          study_accession = xml_attr(xml_find_first(doc, "//STUDY"), "accession"),
          title = safe_extract_xml2("//STUDY_TITLE", doc),
          abstract = safe_extract_xml2("//STUDY_ABSTRACT", doc),
          description = safe_extract_xml2("//STUDY_DESCRIPTION", doc),
          study_type = xml_attr(xml_find_first(doc, "//STUDY_TYPE"), "existing_study_type"),
          center = xml_attr(xml_find_first(doc, "//STUDY"), "center_name"),
          submission_date = xml_attr(xml_find_first(doc, "//STUDY"), "created")
        )

        results[[accession]] <- study_info

      } else {
        cat("No results found for", accession, "\n")
        results[[accession]] <- list(accession = accession, error = "No results found")
      }

    }, error = function(e) {
      cat("Error processing", accession, ":", e$message, "\n")
      results[[accession]] <- list(accession = accession, error = e$message)
    })

    Sys.sleep(3)  # Rate limiting
  }

  return(results)
}

metadata_to_dataframe <- function(metadata_list) {
  df_list <- lapply(names(metadata_list), function(acc) {
    study <- metadata_list[[acc]]
    data.frame(
      query_accession = acc,
      study_accession = ifelse(is.null(study$study_accession) || is.na(study$study_accession),
                              acc, study$study_accession),
      title = ifelse(is.null(study$title), NA, study$title),
      abstract = ifelse(is.null(study$abstract), NA, study$abstract),
      description = ifelse(is.null(study$description), NA, study$description),
      study_type = ifelse(is.null(study$study_type), NA, study$study_type),
      center = ifelse(is.null(study$center), NA, study$center),
      submission_date = ifelse(is.null(study$submission_date), NA, study$submission_date),
      error = ifelse(is.null(study$error), NA, study$error),
      stringsAsFactors = FALSE
    )
  })

  do.call(rbind, df_list)
}

harvest_bundle_metadata <- function(org) {
  bundle_path <- paste("/mnt/hdd1/dee2/sradb/big_proj/",org,sep="")
  zips <- list.files(bundle_path,pattern="zip$")
  srps <- sapply(strsplit(zips,"_"),"[[",1)
  zips <- zips[which(! duplicated(srps))] # exclude duplicate bundles without GSE info
  srps <- srps[which(! duplicated(srps))]
  gse <- gsub(".zip","",sapply(strsplit(zips,"_"),"[[",2))
  myfilename <- paste("../sradb/",org,"_srp.tsv",sep="")
  file.copy(myfilename,"tmp0",overwrite=TRUE)
  system("cut -f1 tmp0  > tmp1")
  srp_existing <- gsub('"',"",readLines("tmp1"))
  srps_new <- setdiff(srps,srp_existing)

  if ( length(srps_new) > 0 ) {
    res2 <- get_sra_studies_metadata_xml2(srps_new)
    res2df <- metadata_to_dataframe(res2)
    res2df$GSE <- gse[which(srps %in% res2df$query_accession)]
    zips2 <- zips[which(srps %in% res2df$query_accession)] # only include bundles with metadata
    res2df$URL <- paste("https://dee2.io/huge/",org,"/",zips2,sep="")
    write.table(x=res2df,file=myfilename,sep="\t",row.names=FALSE, append=TRUE)
    SYSCOMMAND <- gsub("myorg",org,"scp -i ~/.ssh/dee2_2025 ../sradb/myorg_srp.tsv ubuntu@dee2.io:/dee2_data/metadata/")
    system(SYSCOMMAND)
    unlink("tmp1")
    unlink("tmp0")
  }
}

harvest_bundle_metadata(org)

```


## Session information

```{r,session}

sessionInfo()

```
