---
title: "Regular update for DEE2 database"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 7
theme: cosmo
params:
  org: "NULL"
---

## Intro

This script updates the DEE2 database with the newly processed datasets.
It is important for QC and aggregating the datasets.

Notes

* if an error occurs on here: mclapply(fin_new,check_contents,gre,tre,mc.cores=CORES)
 then need to run this rm -rf `find ../data/org | grep tmp$ | head -1000`

Set the organism

The following code can take user supplied arguments and run the pipeline.

```
args = commandArgs(trailingOnly=TRUE)
org=args[1]
print(org)
```

We could run this as a for loop from bash

```
for ORG in athaliana osativa zmays celegans dmelanogaster drerio rnorvegicus scerevisiae ecoli hsapiens mmusculus
bdistachyon gmax hvulgare ptrichocarpa sbicolor slycopersicum stuberosum taestivum vvinifera ; do

  Rscript -e rmarkdown::render('dee_pipeline.Rmd',params=list(org = "$ORG"))

done

```

It can also be run in R like this:

```
#rmarkdown::render("dee_pipeline.Rmd",params=list(org = "ecoli"))
```


```{r,begin}

setwd("/mnt/hdd1/dee2/code")

library("parallel")
library("data.table")
library("R.utils")
library("reutils")
library("XML")
library("rjson")
library("rhdf5")
library("reutils")
library("ff")

IPADD="118.138.235.221"

CORES=5

args = commandArgs(trailingOnly=TRUE)
org=params$org
#org
#org="ecoli"

species_list <- c("3702", "4530", "4577", "6239", "7227", "7955",
  "562", "9606", "10090", "10116", "4932",
  "15368", "3847", "1753", "3694", "4558",
  "1753", "4113", "4565", "1753")

#now annotate the short names 
names(species_list) <- c("athaliana", "osativa", "zmays",
  "celegans", "dmelanogaster", "drerio",
  "ecoli", "hsapiens", "mmusculus", "rnorvegicus", "scerevisiae",
  "bdistachyon", "gmax", "hvulgare", "ptrichocarpa", "sbicolor",
  "slycopersicum", "stuberosum", "taestivum", "vvinifera")

taxa_name <- species_list[[org]]

species_names <- c("'Arabidopsis thaliana'", "'Oryza sativa'",
  "'Zea mays'", "'Caenorhabditis elegans'",
  "'Drosophila melanogaster'", "'Danio rerio'",
  "'Escherichia coli'", "'Homo sapiens'", "'Mus musculus'",
  "'Rattus norvegicus'", "'Saccharomyces cerevisiae'",
  "'Brachypodium distachyon'", "'Glycine max'",
  "'Hordeum vulgare'", "'Populus trichocarpa'",
  "'Sorghum bicolor'","'Solanum lycopersicum'",
  "'Solanum tuberosum'", "'Triticum aestivum'",
  "'Vitis vinifera'")

#now annotate the short names 
names(species_names)<- c("athaliana", "osativa", "zmays",
  "celegans", "dmelanogaster", "drerio",
  "ecoli", "hsapiens", "mmusculus", "rnorvegicus", "scerevisiae",
  "bdistachyon", "gmax", "hvulgare", "ptrichocarpa", "sbicolor",
  "slycopersicum", "stuberosum", "taestivum", "vvinifera")

species_name <- species_names[[org]]

print(org)

#number of protein coding genes from ensembl
numgenes <- c(27655, 35806, 39756, 20362, 13918, 25903, 4140, 20338, 22598, 22250, 6692,
  34310, 55897, 35826, 34699, 34118, 34658, 39021, 107891, 37480)

names(numgenes) <- c("athaliana", "osativa", "zmays",
  "celegans", "dmelanogaster", "drerio",
  "ecoli", "hsapiens", "mmusculus", "rnorvegicus", "scerevisiae",
  "bdistachyon", "gmax", "hvulgare", "ptrichocarpa", "sbicolor",
  "slycopersicum", "stuberosum", "taestivum", "vvinifera")

numgenes = numgenes[[org]]

###Set some directories
CODEWD = getwd()
DATAWD = paste(normalizePath("../data/"),org,sep="/")
SRADBWD = normalizePath("../sradb/")
MXDIR = normalizePath("../mx/")
QUEUEWD = normalizePath("../queue/")

### Set years range
YEARS=2000:2026

```

## Get metadata from SRA

The metadata is obtained by date to make each request smaller and more reliable.
This also allows for quicker updates, as dates that have already been fetched do not need to be done again.

```{r,fetchmetadata}

MY_SRA_CMD <- paste('bash metadata_dl_full.sh', org)
MY_SRA_CMD
system(MY_SRA_CMD)

mdfiles <- list.files(paste(SRADBWD,"/",org,sep=""),recursive=TRUE,full.names=TRUE)

metadata_lines <-  lapply(mdfiles, function(x) {
  readLines(x)
})

mdfiles <- mdfiles[which(lapply(metadata_lines,length)>1)]

sra_metadata <-  lapply(mdfiles, function(x) {
  y <- read.csv(x)
})


#sra_metadata <-  lapply(mdfiles, function(x) {
#  y <- read.csv(x)
#  z <- length(which(colnames(y) == "pool_member_spots"))
#  if ( z == 1 ) {
#    y$pool_member_spots = NULL
#  }
#  if ( ncol(y) == 15 ) {
#    return(y)
#  }
#})

md_df <- do.call(rbind,sra_metadata)
CSVOLD=paste(SRADBWD,"/",org,"_old.csv",sep="")
CSVNEW=paste(SRADBWD,"/",org,"_new.csv",sep="")

if (file.exists(CSVNEW)) {
  renameFile(CSVNEW,CSVOLD,overwrite=TRUE)
}

write.csv(md_df,CSVNEW)

accessions <- as.data.frame(cbind(md_df$experiment_accession,
  md_df$study_accession,
  md_df$sample_accession,
  md_df$run_accession))

nrow(accessions)
colnames(accessions) <- c("experiment","study","sample","run")
runs <- accessions$run
source("dee_pipeline_functions.R")

```

## Now determine which datasets have already been processed and completed

```{r,check_presence_new_datasets}

unlink(list.files(DATAWD,pattern="_STARtmp",recursive=T))

folders <- list.files(DATAWD,full.names=T,pattern="RR")
fin_new <- paste(DATAWD,sapply(strsplit(list.files(path = DATAWD, pattern = "finished" ,
  full.names = T, recursive = T),"/"),"[[",7),sep="/")
fin_new <- fin_new[grep("RR",fin_new)]
val_old <- paste(DATAWD,sapply(strsplit(list.files(path = DATAWD, pattern = "validated" ,
  full.names = T, recursive = T),"/"),"[[",7),sep="/")

# delete folders that are not expected as they are not in known runs
expected_folders <- paste(DATAWD,runs,sep="/")
unexpected_folders <- setdiff(folders,expected_folders)
write(unexpected_folders,file=paste(DATAWD,"/unexpected_folders.txt",sep=""))

# move unexpected folders to a trash location
allocated <- union(fin_new,val_old)
unalloc <- setdiff(folders,allocated)
lapply( unalloc, function(x) {
  file.copy( x ,  paste(DATAWD,"/trash/",sep="") , recursive=TRUE )
  unlink(x,recursive=TRUE)
} )
#unlink(unalloc,recursive=TRUE)

#Expected rows of se and ke files
gre <- dim( read.table(paste(DATAWD,"/rownames_gene.txt",sep=""),header=TRUE, comment.char="") )[1]
tre <- dim( read.table(paste(DATAWD,"/rownames_tx.txt",sep=""),header=TRUE, comment.char="") )[1]

message("run the check of new datasets")
source("dee_pipeline_functions.R")

mclapply(fin_new,check_contents,gre,tre,mc.cores=CORES)
message("done")

val <- unique(paste(DATAWD,sapply(strsplit(list.files(path = DATAWD, pattern = "validated" ,
  full.names = T, recursive = T),"/"),"[[",7),sep="/"))
runs_done <- sapply(strsplit(val,"/"),"[[",7)

se_files <- paste( DATAWD , "/" , runs_done , "/" , runs_done , ".se.tsv.gz",sep="")

print(paste(length(runs_done),"runs completed"))
runs_todo <- base::setdiff(runs, runs_done)
print(paste(length(runs_todo),"runs in the queue"))

# Cut the queue and flip order sometimes, so that we can analyse different runs
# and not just process the same ones again and again
CUTPOINT = sample(1:length(runs_todo),1)
runs_todo <- runs_todo[c(CUTPOINT:length(runs_todo),1:(CUTPOINT-1))]
ORIENTATION <- as.numeric(format(Sys.time(), "%s")) %% 2
if ( ORIENTATION == 0 ) {  runs_todo <- rev(runs_todo) }

#Update queue on webserver if older than
queue_name = paste(QUEUEWD,"/",org,".queue.txt",sep="")
write.table(runs_todo,queue_name,quote=F,row.names=F,col.names=F)
SCP_COMMAND = paste("scp -i ~/.ssh/dee2_2026 ",queue_name ," ubuntu@118.138.235.221:~/Public")
system(SCP_COMMAND)

#Update metadata on webserver
accessions_done <- accessions[which(accessions$run %in% runs_done),] #thisline audit
write.table(accessions_done,file=paste(SRADBWD,"/",org,"_accessions.tsv",sep=""),quote=F,row.names=F)

save.image(file = paste(org,".RData",sep=""))

```

## Get GEO metadata information

The GEO information is already in the md_df object. Winning!

```{r,tidymetadata1}

QC_summary <- "NA"

#extract out the important accessions in order
x2 <- as.data.frame(cbind(md_df$run_accession, QC_summary, md_df$experiment_accession,
  md_df$sample_accession, md_df$study_accession, md_df$experiment_title,
  md_df$geo_series), stringsAsFactors=FALSE)

colnames(x2) <- c("SRR_accession","QC_summary","SRX_accession","SRS_accession",
  "SRP_accession","Experiment_title","GEO_series")

# NA values replaced with blank
x2[is.na(x2)] <- ""

#write out the accession number info and upload to webserver
write.table(x2,file=paste(SRADBWD,"/",org,"_metadata.complete.tsv.cut",sep=""),
  quote=F,sep="\t",row.names=F)
x2 <- x2[which(x2$SRR_accession %in% runs_done),]

# write the srpqueue to enable new request from users
srpqueue <- accessions[which(! accessions$run %in% x2$SRR_accession),2]
srpqueue <- unique(srpqueue)
srpqueue <- srpqueue[order(srpqueue)]
srpqueuename = paste(SRADBWD,"/",org,"_srpqueue.txt",sep="")
writeLines(srpqueue,con=srpqueuename)
SCP_COMMAND=paste("scp -i ~/.ssh/dee2_2026", srpqueuename ,
    " ubuntu@118.138.235.221:/dee2_data/srpqueue")
system(SCP_COMMAND)

```

## Quality control

```{r,qc1}

source("dee_pipeline_functions.R")
library("parallel")

CORES=4

# this line was giving some errors with mouse data - now executes in batches
myaccessions <- x2$SRR_accession
length(myaccessions)
qc_res=NULL
chunksize=200

qc_res <- unlist(lapply(myaccessions, qc_analysis, org=org))

x2$QC_summary <- qc_res

# select datasets with qcfile
dim(x2)
x2 <- x2[which(x2$QC_summary!="QC FILE NOT FOUND"),]
dim(x2)

# write metadata
write.table(x2,file=paste(SRADBWD,"/",org,"_metadata.tsv.cut",sep=""),
  quote=F,sep="\t",row.names=F)

```

## Data aggregation

SE, KE, then QC files in HDF5 format.

```{r,dataagg_hdf5}

CORES=8

h5file <- paste(org,"_se.h5",sep="")
if (file.exists(h5file)) { file.remove(h5file) }
h5createFile(h5file)
srr <- x2$SRR_accession
file_list <- paste("/mnt/hdd1/dee2/data/",org,"/",srr,"/",srr,".se.tsv.gz",sep="")
batch_size <- 500
num_files <- length(file_list)
rows_per_file <- nrow(read.table(file_list[1],row.names=1,header=TRUE))
num_cols <- 1
h5createDataset(
  file = h5file,
  dataset = "bigmatrix",
  dims = c(num_files, rows_per_file),
  storage.mode = "integer",
  chunk = c(10, rows_per_file),    # 10,000-row chunks
  level = 9                      # compression level (gzip)
)
for (i in seq(1, length(file_list), by = batch_size)) {
  batch_files <- file_list[i:min(i + batch_size - 1, length(file_list))]
  data_list <- mclapply(batch_files, function(f) {
    t(as.matrix(read.table(f,header=TRUE,row.names=1)[,1]))
  } , mc.cores=CORES )
  batch_data <- do.call(rbind, data_list)
  row_start <- (i - 1) + 1
  row_end <- row_start + nrow(batch_data) - 1
  h5write(batch_data, h5file, "bigmatrix", index = list(row_start:row_end, 1:rows_per_file ))
  cat(sprintf("Processed files %d to %d\n", i, i + length(batch_files) - 1))
}
myrownames <- sapply(strsplit(basename(file_list),"\\."),"[[",1)
h5write(myrownames, h5file,"rownames")
mycolnames <- rownames( read.table(file_list[1]) )
h5write(mycolnames, h5file, "colnames")
H5close()
system(paste('rsync -azh -e \"ssh -i  ~/.ssh/dee2_2026 \" ', h5file ,' ubuntu@dee2.io:/dee2_data/bulk/',sep=""))
copyFile(h5file,"../mx/",overwrite=TRUE)
unlink(h5file)

# NOW FOR THE KE TSV DATASET
h5file <- paste(org,"_ke.h5",sep="")
if (file.exists(h5file)) { file.remove(h5file) }
h5createFile(h5file)
file_list <- paste("/mnt/hdd1/dee2/data/",org,"/",srr,"/",srr,".ke.tsv.gz",sep="")
batch_size <- 500
num_files <- length(file_list)
rows_per_file <- nrow(read.table(file_list[1],row.names=1,header=TRUE))
num_cols <- 1
 h5createDataset(
  file = h5file,
  dataset = "bigmatrix",
  dims = c(num_files, rows_per_file),
  storage.mode = "double",
  chunk = c(10, rows_per_file),    # 10,000-row chunks
  level = 9                      # compression level (gzip)
)
for (i in seq(1, length(file_list), by = batch_size)) {
  batch_files <- file_list[i:min(i + batch_size - 1, length(file_list))]
  data_list <- mclapply(batch_files, function(f) {
    t(as.matrix(read.table(f,header=TRUE,row.names=1)[,3]) )
  } , mc.cores=CORES )
  batch_data <- do.call(rbind, data_list)
  row_start <- (i - 1) + 1
  row_end <- row_start + nrow(batch_data) - 1
  h5write(batch_data, h5file, "bigmatrix", index = list(row_start:row_end, 1:rows_per_file ))
  cat(sprintf("Processed files %d to %d\n", i, i + length(batch_files) - 1))
}
myrownames <- sapply(strsplit(basename(file_list),"\\."),"[[",1)
h5write(myrownames, h5file, "rownames")
mycolnames <- rownames( read.table(file_list[1]) )
h5write(mycolnames, h5file, "colnames")
H5close()
system(paste('rsync -azh -e \"ssh -i  ~/.ssh/dee2_2026 \" ', h5file ,' ubuntu@dee2.io:/dee2_data/bulk/',sep=""))
copyFile(h5file,"../mx/",overwrite=TRUE)
unlink(h5file)

## Next is the QC data
h5file <- paste(org,"_qc.h5",sep="")
if (file.exists(h5file)) { file.remove(h5file) }
h5createFile(h5file)
file_list <- paste("/mnt/hdd1/dee2/data/",org,"/",srr,"/",srr,".qc",sep="")
batch_size <- 10000
qc <- read.csv(file_list[1],row.names=1,header=FALSE,sep=":")
num_files <- length(file_list)
rows_per_file <- nrow(read.csv(file_list[1],row.names=1,header=FALSE,sep=":"))
num_cols <- 1
h5createDataset(
  file = h5file,
  dataset = "bigmatrix",
  dims = c(num_files, rows_per_file),
  storage.mode = "character",
  chunk = c(100, rows_per_file),
  level = 9
)
for (i in seq(1, length(file_list), by = batch_size)) {
  batch_files <- file_list[i:min(i + batch_size - 1, length(file_list))]
  data_list <- mclapply(batch_files, function(f) {
    t(as.matrix( read.csv(f,row.names=1,header=FALSE,sep=":") ) )
  } , mc.cores=CORES )
  batch_data <- do.call(rbind, data_list)
  row_start <- (i - 1) + 1
  row_end <- row_start + nrow(batch_data) - 1
  h5write(batch_data, h5file, "bigmatrix", index = list(row_start:row_end, 1:rows_per_file ))
  cat(sprintf("Processed files %d to %d\n", i, i + length(batch_files) - 1))
}
myrownames <- sapply(strsplit(basename(file_list),"\\."),"[[",1)
h5write(myrownames, h5file, "rownames")
mycolnames <- rownames( read.table(file_list[1]) )
h5write(mycolnames, h5file, "colnames")
H5close()
system(paste('rsync -azh -e \"ssh -i  ~/.ssh/dee2_2026 \" ', h5file ,' ubuntu@dee2.io:/dee2_data/bulk/',sep=""))
copyFile(h5file,"../mx/",overwrite=TRUE)
unlink(h5file)

```

Make md5sums and send to server.

```{r,dataagg_legacy}

#aggregate se ke and qc data
CMD=paste("./dee_pipeline.sh",org)
system(CMD)

```

## Transfer the data files to the webserver

Calculate which datasets need to be uploaded, then collect them in a single folder on the host.
Then copy them all over in one rsync command.

```{r,transfer1}

CMDX=paste('ssh -i ~/.ssh/dee2_2026 ubuntu@dee2.io "ls /dee2_data/data/',org,'"' , sep="")
svr_contents <- system(CMDX, intern=TRUE)
rr_contents <- svr_contents[grep("RR",svr_contents)]
to_transfer <- x2$SRR_accession[which(!x2$SRR_accession %in% rr_contents)]

dest_path <- paste("/mnt/hdd1/dee2/tmp","/",org,sep="")
if ( ! file.exists(dest_path) ) { dir.create(dest_path) }

lapply(to_transfer, function(srr) {
  origin_path <- paste("/mnt/hdd1/dee2/data/",org,"/",srr,sep="")
  file.copy(origin_path,dest_path,recursive=TRUE)
})

ll <- list.files(dest_path,recursive=TRUE,full.names=TRUE)
to_delete <- ll[grep("gz$",ll)]
lapply(to_delete,unlink)
rsync_command <- "rsync -azh -e \"ssh -i  ~/.ssh/dee2_2026 \" /mnt/hdd1/dee2/tmp/ORG ubuntu@dee2.io:/dee2_data/data/"
rsync_command <- gsub("ORG",org,rsync_command)
system(rsync_command)
unlink(dest_path,recursive=TRUE)

#now attach the additional metadata and upload
x <- x2[,c("SRR_accession","QC_summary","SRX_accession","SRS_accession","SRP_accession","GEO_series","Experiment_title")]

x <- x[which(x$SRR_accession %in% runs_done),]
x <- apply(x,2,as.character)
x <- gsub("\r?\n|\r", " ", x)
write.table(x,file=paste(SRADBWD,"/",org,"_metadata.tsv",sep=""),quote=F,sep="\t",row.names=F)

SCP_COMMAND=paste("scp -i ~/.ssh/dee2_2026 ", paste(SRADBWD,"/",org,"_metadata.tsv",sep="") , " ubuntu@dee2.io:/dee2_data/metadata")
system(SCP_COMMAND)

SCP_COMMAND=paste("scp -i ~/.ssh/dee2_2026 ", paste(SRADBWD,"/",org,"_metadata.tsv.cut",sep="") , " ubuntu@dee2.io:/dee2_data/metadata")
system(SCP_COMMAND)

CHMOD_COMMAND <- paste("ssh -i ~/.ssh/dee2_2026 ubuntu@118.138.235.221 'chmod +x /dee2_data/data/ORG'")
CHMOD_COMMAND <- gsub("ORG",org,CHMOD_COMMAND)
system(CHMOD_COMMAND)

save.image(file = paste(org,".RData",sep=""))

```

## Update the dataset numbers on the dee2.io website

This is the last step.

```{r, updatepng}

source("website_update.R")

```

## Update bundles for this organism

```{r,bundles}

CMD_BUNDLES <- paste("bash bundles.sh",org)
system(CMD_BUNDLES)

library(rentrez)
library(xml2)
library(jsonlite)

get_sra_studies_metadata_xml2 <- function(study_accessions) {
  results <- list()
  for (accession in study_accessions) {
    cat("Fetching:", accession, "\n")
    tryCatch({
      # Search for the study
      search_result <- entrez_search(
        db = "sra",
        term = paste0(accession, "[Accession]"),
        retmax = 100
      )
      if (length(search_result$ids) > 0) {
        # Fetch XML data
        xml_data <- entrez_fetch(
          db = "sra",
          id = search_result$ids[1],
          rettype = "xml"
        )
        # Parse XML with xml2
        doc <- read_xml(xml_data)
        # Helper function to safely extract values
        safe_extract_xml2 <- function(xpath_expr, doc) {
          result <- xml_find_all(doc, xpath_expr)
          if (length(result) == 0) {
            return(NA)
          } else if (grepl("@", xpath_expr)) {
            # It's an attribute
            return(xml_text(result[1]))
          } else {
            # It's an element
            return(xml_text(result[1]))
          }
        }
        study_info <- list(
          accession = accession,
          study_accession = xml_attr(xml_find_first(doc, "//STUDY"), "accession"),
          title = safe_extract_xml2("//STUDY_TITLE", doc),
          abstract = safe_extract_xml2("//STUDY_ABSTRACT", doc),
          description = safe_extract_xml2("//STUDY_DESCRIPTION", doc),
          study_type = xml_attr(xml_find_first(doc, "//STUDY_TYPE"), "existing_study_type"),
          center = xml_attr(xml_find_first(doc, "//STUDY"), "center_name"),
          submission_date = xml_attr(xml_find_first(doc, "//STUDY"), "created")
        )
        results[[accession]] <- study_info
      } else {
        cat("No results found for", accession, "\n")
        results[[accession]] <- list(accession = accession, error = "No results found")
      }
    }, error = function(e) {
      cat("Error processing", accession, ":", e$message, "\n")
      results[[accession]] <- list(accession = accession, error = e$message)
    })
    Sys.sleep(10)  # Rate limiting
  }
  return(results)
}

metadata_to_dataframe <- function(metadata_list) {
  df_list <- lapply(names(metadata_list), function(acc) {
    study <- metadata_list[[acc]]
    data.frame(
      query_accession = acc,
      study_accession = ifelse(is.null(study$study_accession) || is.na(study$study_accession),
                              acc, study$study_accession),
      title = ifelse(is.null(study$title), NA, study$title),
      abstract = ifelse(is.null(study$abstract), NA, study$abstract),
      description = ifelse(is.null(study$description), NA, study$description),
      study_type = ifelse(is.null(study$study_type), NA, study$study_type),
      center = ifelse(is.null(study$center), NA, study$center),
      submission_date = ifelse(is.null(study$submission_date), NA, study$submission_date),
      error = ifelse(is.null(study$error), NA, study$error),
      stringsAsFactors = FALSE
    )
  })
  do.call(rbind, df_list)
}

harvest_bundle_metadata <- function(org) {
  bundle_path <- paste("/mnt/hdd1/dee2/sradb/big_proj/",org,sep="")
  zips <- list.files(bundle_path,pattern="zip$")
  srps <- sapply(strsplit(zips,"_"),"[[",1)
  zips <- zips[which(! duplicated(srps))] # exclude duplicate bundles without GSE info
  srps <- srps[which(! duplicated(srps))]
  gse <- gsub(".zip","",sapply(strsplit(zips,"_"),"[[",2))
  myfilename <- paste("../sradb/",org,"_srp.tsv",sep="")
  file.copy(myfilename,"tmp0",overwrite=TRUE)
  system("cut -f1 tmp0  > tmp1")
  srp_existing <- gsub('"',"",readLines("tmp1"))
  srps_new <- setdiff(srps,srp_existing)

  if ( length(srps_new) > 0 ) {
    res2 <- get_sra_studies_metadata_xml2(srps_new)
    res2df <- metadata_to_dataframe(res2)
    res2df$GSE <- gse[which(srps %in% res2df$query_accession)]
    zips2 <- zips[which(srps %in% res2df$query_accession)] # only include bundles with metadata
    res2df$URL <- paste("https://dee2.io/huge/",org,"/",zips2,sep="")
    write.table(x=res2df,file=myfilename,sep="\t",row.names=FALSE, append=TRUE)
    SYSCOMMAND <- gsub("myorg",org,"scp -i ~/.ssh/dee2_2026 ../sradb/myorg_srp.tsv ubuntu@dee2.io:/dee2_data/metadata/")
    system(SYSCOMMAND)
    unlink("tmp1")
    unlink("tmp0")
  }
}

harvest_bundle_metadata(org)

```


## Session information

```{r,session}

sessionInfo()

```
